A Horrocks-type theorem for even orthogonal $K_2$

### 2019-09-30 dl-paper.tex
Minor

\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under conjugation by $x_\alpha(aX^{-1})$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $K(\alpha, \beta)$ and $Z_{\alpha, \beta}$. \end{lemma}
\begin{proof} To simplify notation we call the generators of the subgroup $Z_{\alpha,\beta}$ ``generators of type Z``. By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is either the generator itself or a product of generators of type Z, Z, 1. \cref{Crels} also shows that the conjugate to a generator of type 5 is either the generator itself or a product of generators of type Z, Z, 5.

@@

\begin{lemma} \label{conj-K-a-b} For $b \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(b)} \subseteq K(\alpha, \beta)$. \end{lemma}
\begin{proof} By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(b)$ either coincides with $g$ or is a product of generators of type 4, 1, 1. Now if $g = x_\epsilon(Xf)$, $\epsilon \in \{\pm \alpha, \pm \beta\}$ is a generator of type 2 or 3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type 2 or 3. By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate to a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1. Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$. \end{proof}

\begin{lemma} For $g \in K(\alpha, \beta)$ and $a, b\in A$ the conjugate to $S_\alpha(a, g)$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. \end{lemma}
\begin{proof} By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it remains to show that the conjugate to each generator $g = z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. Throughout the proof we understand generator types according to~\cref{defP0}. It is clear that $g$ itself is a generator of type 2, therefore it remains to consider the case $\gamma\not \perp \beta - \alpha$.

>>>>

\begin{lemma} \label{image-K-a-b} The image of $K(\alpha, \beta)$ under conjugation by $x_\alpha(aX^{-1})$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by $K(\alpha, \beta)$ and $Z_{\alpha, \beta}$. \end{lemma}
\begin{proof} To simplify notation we call the generators of the subgroup $Z_{\alpha,\beta}$ ``generators of type Z``. By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate of a generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is either the generator itself or a product of generators of type Z, Z, 1. \cref{Crels} also shows that the conjugate of a generator of type 5 is either the generator itself or a product of generators of type Z, Z, 5.

@@

\begin{lemma} \label{conj-K-a-b} For $b \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(b)} \subseteq K(\alpha, \beta)$. \end{lemma}
\begin{proof} By~\cref{Zrels} the conjugate of a generator $g = z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(b)$ is either $g$ itself or a product of generators of type 4, 1, 1. By~\cref{Crels} the conjugate of a generator $g = c_\delta(f, X\xi)$ of type 5 is either $g$ or a product of generators of type 5, 4, 1.

Now if $g = x_\gamma(Xf)$, $\gamma \in \{\pm \alpha, \pm \beta\}$ is a generator of type 2 or 3, the conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two generators of type 2 or 3.  Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, b) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$. \end{proof}

\begin{lemma} For $g \in K(\alpha, \beta)$ and $a, b\in A$ the conjugate of $S_\alpha(a, g)$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. \end{lemma}
\begin{proof} By~\cref{image-K-a-b} and~\cref{conj-K-a-b} it remains to show that the conjugate of each generator $g = z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ of $Z_{\alpha, \beta}$ by $x_{\beta-\alpha}(b)$ belongs to $P_\alpha(0)$. Throughout the proof we understand generator types according to~\cref{defP0}. It is clear that $g$ itself is a generator of type 2, therefore it remains to consider the case $\gamma\not \perp \beta - \alpha$.
